Computer Science House Constitution

### 2024-04-15 constitution.tex
Fix ordering in budget allocation table (#221)
Update constitution.tex (#222)
Small fixes for grammar, formatting, and organization (#223)

% ARTICLE 3 - CONSTITUTIONAL STRUCTURE
\article{Constitutional Structure and Amendment}

@@

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted during the week.
The final proposal is presented the following week and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.

% ARTICLE 4 - MEMBERSHIP
\article{Membership}
There are five types of membership available to CSH.
When describing membership types, the following terms are used:
\begin{description}
	\item[Qualifications:] What criteria an applicant needs to be eligible for membership
	\item[Selection:] The process by which an applicant gains membership
	\item[Expectations:] The duties and responsibilities associated with CSH membership
	\item[Privileges:] The benefits offered to members
	\item[Evaluations:] The process by which a member is reviewed and assessed
	\item[Leave of Absence:] The process by which a member may leave CSH during an RIT Leave of Absence
	\item[Resignations:] The process by which a member terminates CSH membership
	\item[Term:] The duration of the membership
\end{description}

@@

\asubsection{Introductory Membership Expectations}
Intro Members are expected to meet all the requirements of the Intro Process, as described in \ref{Expectations of an Introductory Member}.
Intro Members are not required to pay membership dues.

@@

\asubsubsubsection{Voting}
On a member-by-member basis, the Intro Eval determines if each Intro Member has successfully completed the Intro Process requirements \ref{Expectations of an Introductory Member}.
An Immediate Relative Majority Vote with two-thirds quorum is required for the Eval to be valid.
For an Active Member to be eligible to vote during the Intro Eval they must meet the requirements outlined in \ref{Expectations of Voting Members}.
Neither absentee nor proxy votes are allowed.
Intro Members may be offered any of the outcomes listed in \ref{Outcomes}

@@

\asubsection{Introductory Membership Resignations}
Intro Members may resign by submitting the request for termination of membership to the Chair or the Evals Director in writing before the completion of the Intro Process.

@@

\asubsection{Active Membership Selection}
Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evals Director. They will retain their previous Housing Status if applicable.
\\*\\*
Any Alumni Member in bad standing, as described in \ref{Alumni Membership Selection}, may become an Active Member by notifying the Evals Director of their intent to participate.
The Evals Director will then bring them up for an Immediate Relative Majority vote with fifty percent quorum at the next House Meeting.
If the vote passes the Alumni is reinstated as an Active Member with Off-Floor Status effective immediately.

@@

\asubsection{Active Membership Evaluations}
Active Members are evaluated annually through the Eval Process as described in \ref{Evaluations Processes}.

% ACTIVE MEMBERSHIP EVALUATIONS
\asubsubsection{Evaluations Processes}
During the academic year, an Active Member is evaluated by the Membership Eval.
The Membership Eval is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
These meetings are open only to Active Members.
All Active Members are expected to attend these Evals meetings.
\\* \\*
At the beginning of any Eval Process listed herein, the Evals Director must read the sections of the CSH Constitution used during the respective Eval Process.
It is incumbent upon each member to provide the Evals Director with whatever information they feel is necessary to ensure an accurate evaluation.

\asubsubsubsection{Membership Evaluation}
The Membership Eval occurs once per academic year.
It is performed as part of the Eval Process that takes place during the spring semester to comply with RIT Housing deadlines.

\asubsubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of Active Members} at the beginning of the Membership Eval passes their Membership Eval without being voted on.
All Active Members who have not received an exemption from E-Board prior to the Membership Eval will be evaluated on a member-by-member basis by Active Members.
The Membership Eval shall hold members to the objective requirements defined in \ref{Expectations of Active Members} and determine which members may continue as an Active Member in the following academic year.
Exceptions to the requirements may be made, as attending members may choose any of the outcomes for each member, even if the member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Eval occurs.
A Secret Immediate Relative Majority vote with two-thirds quorum is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

\asubsubsubsubsection{Outcomes}
Members who pass the Membership Eval have the option to participate as an Active Member in the following year.
\\* \\*
If a member fails and has never passed a Membership Eval in the past, their membership will be revoked immediately.
If the member fails, but has previously passed a Membership Eval, they will move to Alumni Membership in bad standing, as defined in \ref{Alumni Membership Selection}, at the end of the Standard Operating Session.
In either case, the member forfeits their ability to participate as an Active Member in the following year.
\\* \\*
A member may be given a conditional to complete as a means of making up for missing requirements.
A conditional may be proposed by any member present at the Eval.
If the conditional is approved by the Evals Director, it is then voted on by the attending members as described in \ref{Voting}.
Each conditional consists of a set of additional requirements and a deadline for completing them.
Members who are given a conditional have their Eval decision deferred, and therefore maintain their current membership status until the conditional is resolved.
When the deadline expires, the conditional will be brought before E-Board, who will assess its completeness.
A conditional member who does not meet these additional requirements will have failed the Eval.

\asubsubsubsection{Appeals Process}
If a member disagrees with the outcome of any Eval and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
\\* \\*
If the member is still unsatisfied after being heard by E-Board, the appeal may be brought to the attention of the ResLife Advisor.

@@

\asubsection{Active Membership Resignations}
An Active Member may resign by submitting, in writing, the reason for resignation to the Chair or the Evals Director.
Instead of forfeiting membership, Active Members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.

@@

\asubsection{Alumni Membership Selection}
Active Members who resign from CSH after passing the current operating session's Membership Eval are considered to be Alumni in good standing.
\\*\\*
Active Members who depart house without passing the current operating session's Membership Eval are considered to be Alumni in bad standing.
This may be appealed to E-Board in order to pursue a different outcome, as described in \ref{Appeals}.

@@

\asubsection{Honorary and Advisory Membership Selection}
\begin{enumerate}
	\item A CSH Member submits a nomination to the Evals Director, in writing, for a person they feel is deserving of Honorary or Advisory Membership. The nomination must specify the type of membership the nominee is nominated for.
	\item The Evals Director performs preliminary research on the candidate and presents the findings.
	\item If E-Board decides not to present the nomination at a House Meeting, the selection process ends and the candidate does not become a member.
	\item If the nomination is presented at a House Meeting for discussion. A Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.
	      Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period.
	\item Candidates selected for Honorary Membership are notified of their selection as an Honorary Member and presented with the honor.
	\item Candidates selected for Advisory Membership are notified of their acceptance as CSH Advisors and asked to accept or decline the selection.
\end{enumerate}

@@

\asection{Leave of Absence}
A Leave of Absence offers the option for members to take extended time away from their responsibilities to CSH for any number of personal issues including, but not limited to, physical illness, mental illness, or caregiving for a sick family member.
In order to request a Leave of Absence, a member must follow the RIT policy for Leave of Absence, located at \url{https://www.rit.edu/policies/d021}. Additionally, the member should notify the Evals Director of their Leave, at which point they become exempt from all CSH requirements until they return.

@@

\asubsubsection{Responsibilities of the Executive Board}
\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to CSH
	\item To meet at least weekly during the Standard Operating Session to discuss and report the operations of CSH
	\item To report pertinent information to members at the following House Meeting
	\item To maintain records of the goals defined by each previous E-Board
	\item To act as a Judicial Board as defined in \ref{Judicial}
	\item To review major projects, as defined in \ref{Expectations of Active Members}
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
	\item To respect the privacy of members confiding in E-Board, barring situations related to sexual assault or endangerment of oneself or others
	\item To publish a document at the end of each semester to all members stating CSH's accomplishments of that semester
	      %\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}.
	      %The constitution should remain up to date with current practices.
\end{enumerate}

@@

\asubsubsection{Dual Directors}
Social and R\&D are the only voting E-Board positions that allow for dual directors.

@@

The following special cases cover the operation of dual directors:
\begin{enumerate}
	\item If one of the members in a dual directorship resigns, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
	      The vacated office is then handled like any other vacated office, as referenced in \ref{Executive Board Resignations}.
	\item During an official E-Board Vote, each dual director's vote counts for one half of a vote in the tallying of votes.
	      The members of the dual directorship need not vote the same way in a vote.
	      This cannot be used to give a vote to a position that would not otherwise have one in an E-Board Vote.
	\item A member of a dual directorship may not hold any other Voting E-Board position or the position of Chair.
	      When attendance requirements call for the dual directorship position to be present, at least one of the dual directors must be present to fulfill the requirements.
\end{enumerate}

@@

\asubsubsection{Selection of the Secretary}
E-Board may select any interested Active Member as Secretary.
The selection process can be an informal appointment, or follow an election process similar to other voting E-Board positions.

\asubsection{Executive Board Resignations}
An E-Board Member may resign their position by submitting in writing the reason for resignation to the Chair.
The E-Board resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new director, as described in section \ref{Appointment of an Interim Director}, will begin at that time.
Following a resignation, the selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
To postpone such a selection, the Chair may chair an Immediate Relative Majority Vote during a House Meeting prior to the beginning of the selection process to delay the selection process by a specified amount of time.

@@

% ARTICLE III - GENERAL OPERATIONS OF THE HOUSE
\article{General Operations of the House}

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\asection{Financial Operations of the House}

@@

\asubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
If a member is unable to pay requested dues, they may appeal their situation to the Financial Director.
The Financial Director then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
If the Financial Director decides their situation warrants no action, the member may appeal this decision to E-Board.
If appealed, E-Board may provide an extension and/or reduction to the member.
If the appeal is denied, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
All dues must be collected in full before the annual Membership Eval, as defined in \ref{Membership Evaluation}.
After this date, dues collection is suspended until the start of the next academic year.
\asubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
	\begin{tabular}[c]{|l c|}
		\hline
		Directorship & Percentage of Dues
		\\ \hline
		\hline
		OpComm       & 20\%
		\\ \hline
		R\&D         & 20\%
		\\ \hline
		Social       & 20\%
		\\ \hline
		IMPs         & 15\%
		\\ \hline
		History      & 10\%
		\\ \hline
		Evals        & 5\%
		\\ \hline
		PR           & 5\%
		\\ \hline
		Accumulated  & 5\%
		\\ \hline
	\end{tabular}
\end{center}

@@

% ARTICLE VI - VOTING
\article{Voting}
This section outlines the different types of votes and ballots used to make decisions and defines relevant terminology.

@@

% ARTICLE VII - JUDICIAL
\article{Judicial}
E-Board may approve a request from a member for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among members, or a House interest needs resolution.

>>>>

% ARTICLE III - CONSTITUTIONAL STRUCTURE
\article{Constitutional Structure and Amendment}

@@

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted during the week.
The final proposal is presented the following week, and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.

% ARTICLE IV - MEMBERSHIP
\article{Membership}
There are five types of membership available to CSH.
When describing membership types, the following terms are used:
\begin{description}
	\item[Qualifications:] What criteria an applicant needs to be eligible for membership
	\item[Selection:] The process by which an applicant gains membership
	\item[Expectations:] The duties and responsibilities associated with CSH membership
	\item[Privileges:] The benefits offered to members
	\item[Evaluations:] The process by which a member is reviewed and assessed
	\item[Leave of Absence:] The process by which a member may leave CSH during an RIT Leave of Absence
	\item[Resignations:] The process by which a member terminates CSH membership
	\item[Term:] The duration of the membership
\end{description}

@@

\asubsection{Introductory Membership Expectations}
Intro Members are expected to meet all the requirements of the Intro Process described in \ref{Expectations of an Introductory Member}.
Intro Members are not required to pay membership dues.

@@

\asubsubsubsection{Voting}
On a member-by-member basis, the Intro Eval determines if each Intro Member has successfully completed the Intro Process requirements described in \ref{Expectations of an Introductory Member}.
An Immediate Relative Majority Vote with two-thirds quorum is required for the Eval to be valid.
For an Active Member to be eligible to vote during the Intro Eval they must meet the requirements outlined in \ref{Expectations of Voting Members}.
Neither absentee nor proxy votes are allowed.
Intro Members may be offered any of the outcomes listed in \ref{Outcomes}.

@@

\asubsection{Introductory Membership Resignations}
Intro Members may resign by submitting a request for termination of membership to the Chair or the Evals Director in writing before the completion of the Intro Process.

@@

\asubsection{Active Membership Selection}
Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evals Director. They will retain their previous Housing Status if applicable.
\\*\\*
Any Alumni Member in bad standing, as described in \ref{Alumni Membership Selection}, may become an Active Member by notifying the Evals Director of their intent to participate.
The Evals Director will then bring them up for an Immediate Relative Majority vote with fifty percent quorum at the next House Meeting.
If the vote passes, the Alumni is reinstated as an Active Member with Off-Floor Status effective immediately.

@@

\asubsection{Active Membership Evaluations}
Active Members are evaluated annually through the Eval Process described below.

% ACTIVE MEMBERSHIP EVALUATIONS
\asubsubsection{Membership Evaluation}
The Membership Eval occurs once per academic year, where Active Members are evaluated.
It is performed as part of the Eval Process that takes place during the spring semester to comply with the RIT Housing deadlines.
The Membership Eval is responsible for determining individuals who will have the option to continue Active Membership in the following academic year.
This meeting is open only to Active Members.
All Active Members are expected to attend this meeting.

\asubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of Active Members} at the beginning of the Membership Eval passes their Membership Eval without being voted on.
All Active Members who have not received an exemption from E-Board prior to the Membership Eval will be evaluated on a member-by-member basis by Active Members.
The Membership Eval shall hold members to the objective requirements defined in \ref{Expectations of Active Members} and determine which members may continue as an Active Member in the following academic year.
Exceptions to the requirements may be made, as attending members may choose any of the outcomes for each member, even if the member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Eval occurs.
A Secret Immediate Relative Majority vote with two-thirds quorum is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

\asubsubsubsection{Outcomes}
Members who pass the Membership Eval have the option to participate as an Active Member in the following year.
\\* \\*
If a member fails and has never passed a Membership Eval in the past, their membership will be revoked immediately.
If the member fails, but has previously passed a Membership Eval, they will move to Alumni Membership in bad standing, as defined in \ref{Alumni Membership Selection}, at the end of the Standard Operating Session.
In either case, the member forfeits their ability to participate as an Active Member in the following year.
\\* \\*
A member may be given a conditional to complete as a means of making up for missing requirements.
A conditional may be proposed by any member present at the Eval.
If the conditional is approved by the Evals Director, it is then voted on by the attending members as described in \ref{Voting}.
Each conditional consists of a set of additional requirements and a deadline for completing them.
Members who are given a conditional have their Eval decision deferred, and therefore maintain their current membership status until the conditional is resolved.
When the deadline expires, the conditional will be brought before E-Board, who will assess its completeness.
A conditional member who does not meet these additional requirements will have failed the Eval.

@@

\asubsection{Active Membership Resignations}
An Active Member may resign by submitting, in writing, the reason for resignation to the Chair or the Evals Director.
Instead of forfeiting membership, Active Members who resign may elect to become Alumni as described in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.

@@

\asubsection{Alumni Membership Selection}
Active Members who resign from CSH after passing the current operating session's Membership Eval are considered to be Alumni in good standing.
\\*\\*
Active Members who depart house without passing the current operating session's Membership Eval are considered to be Alumni in bad standing.
This may be appealed to E-Board in order to pursue a different outcome, described in \ref{Appeals}.

@@

\asubsection{Honorary and Advisory Membership Selection}
\begin{enumerate}
	\item A CSH member submits a nomination to the Evals Director, in writing, for a person they feel is deserving of Honorary or Advisory Membership. The nomination must specify the type of membership the nominee is nominated for.
	\item The Evals Director performs preliminary research on the candidate and presents the findings.
	\item If E-Board decides not to present the nomination at a House Meeting, the selection process ends and the candidate does not become a member.
	\item If the nomination is presented at a House Meeting for discussion. A Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.
	      Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period.
	\item Candidates selected for Honorary Membership are notified of their selection as an Honorary Member and presented with the honor.
	\item Candidates selected for Advisory Membership are notified of their acceptance as CSH Advisors and asked to accept or decline the selection.
\end{enumerate}

@@

\asection{Leave of Absence}
A Leave of Absence offers the option for members to take extended time away from their responsibilities to CSH for any number of personal issues including, but not limited to, physical illness, mental illness, or caregiving for a sick family member.
In order to request a Leave of Absence, a member must follow the RIT policy for Leave of Absence located at \url{https://www.rit.edu/policies/d021}.
Additionally, the member should notify the Evals Director of their Leave of Absence, at which point they become exempt from all CSH requirements until they return.

@@

\asubsubsection{Responsibilities of the Executive Board}
\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to CSH, if they are a Voting Member
	\item To meet at least weekly during the Standard Operating Session to discuss and report the operations of CSH
	\item To report pertinent information to members at the following House Meeting
	\item To maintain records of the goals defined by each previous E-Board
	\item To act as a Judicial Board as defined in \ref{Judicial}
	\item To review major projects as defined in \ref{Expectations of Active Members}
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
	\item To respect the privacy of members confiding in E-Board, barring situations related to sexual assault or endangerment of oneself or others
	\item To publish a document at the end of each semester to all members stating CSH's accomplishments of that semester
	      %\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}.
	      %The constitution should remain up to date with current practices.
\end{enumerate}

@@

\asubsubsection{Dual Directors}
Social and R\&D are the only Voting E-Board positions that allow for dual directors.

@@

The following special cases cover the operation of dual directors:
\begin{enumerate}
	\item If one of the members in a dual directorship resigns, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
	      The vacated office is then handled like any other vacated office in accordance with \ref{Executive Board Resignations}.
	\item During an official E-Board Vote, each dual director's vote counts for one half of a vote in the tallying of votes.
	      The members of the dual directorship need not vote the same way in a vote.
	      This cannot be used to give a vote to a position that would not otherwise have one in an E-Board Vote.
	\item A member of a dual directorship may not hold any other Voting E-Board position or the position of Chair.
	      When attendance requirements call for the dual directorship position to be present, at least one of the dual directors must be present to fulfill the requirements.
\end{enumerate}

@@

\asubsubsection{Selection of the Secretary}
E-Board may select any interested Active Member as Secretary.
The selection process can be an informal appointment, or follow an election process similar to other Voting E-Board positions.

\asubsection{Executive Board Resignations}
An E-Board Member may resign their position by submitting in writing the reason for resignation to the Chair.
The E-Board resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new director, as described in \ref{Appointment of an Interim Director}, will begin at that time.
The selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
To postpone such a selection, the Chair may chair an Immediate Relative Majority Vote during a House Meeting prior to the beginning of the selection process to delay the selection process by a specified amount of time.

@@

% ARTICLE VI - GENERAL OPERATIONS OF THE HOUSE
\article{General Operations of the House}

\asection{Financial Operations of the House}

@@

\asubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
If a member is unable to pay requested dues, they may appeal their situation to the Financial Director.
The Financial Director then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
If the Financial Director decides their situation warrants no action, the member may appeal this decision to E-Board.
If appealed, E-Board may provide an extension and/or reduction to the member.
If the appeal is denied, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
All dues must be collected in full before the annual Membership Eval, as defined in \ref{Membership Evaluation}.
After this date, dues collection is suspended until the start of the next academic year.
\asubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
	\begin{tabular}[c]{|l c|}
		\hline
		Directorship & Percentage of Dues
		\\ \hline
		\hline
		OpComm       & 20\%
		\\ \hline
		Social       & 20\%
		\\ \hline
		R\&D         & 20\%
		\\ \hline
		IMPs         & 15\%
		\\ \hline
		History      & 10\%
		\\ \hline
		Evals        & 5\%
		\\ \hline
		PR           & 5\%
		\\ \hline
		Accumulated  & 5\%
		\\ \hline
	\end{tabular}
\end{center}

@@

\asection{Evaluations Processes}
At the beginning of any Eval Process, the Evals Director must read the sections of the CSH Constitution regarding the relevant Eval Process.
It is incumbent upon each member to provide the Evals Director with whatever information they feel is necessary to ensure an accurate evaluation.

\asubsection{Appeals Process}
If a member disagrees with the outcome of any Eval and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
\\* \\*
If the member is still unsatisfied after being heard by E-Board, the appeal may be brought to the attention of the ResLife Advisor.

% ARTICLE VII - VOTING
\article{Voting}
This section outlines the different types of votes and ballots used to make decisions and defines relevant terminology.

@@

% ARTICLE VIII - JUDICIAL
\article{Judicial}
E-Board may approve a request from a member for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among members, or a House interest needs resolution.
